### 2020-12-17 sections/summary.tex
Update summary.tex

I am a PRS in the DPhil in Politics programme in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. Furthermore, I am an Instructor in the Department of Public Administration and Policy at the Faculty of Economics and Management at the Universidad de Santiago, where I have been working since 2014.

>>>>

I am a PRS in the DPhil (PhD) in Politics programme in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. Furthermore, I am an Instructor in the Department of Public Administration and Policy at the Faculty of Economics and Management at the Universidad de Santiago, where I have been working since 2014.
